Hadoop Image Processing Framework

### 2015-03-16 Paper.tex
Fixed a widow.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\textwidth]{files-chart2}
  \caption{Comparing file writers and readers with and without using
    framework}
  \label{fig:files-chart}
\end{figure}

\begin{lstlisting}[caption = Comparing FileWriter instance in java and SequenceBundleWriter instance in Hadoop Image Processing framework ]
//Sample File Writing in Java

File file = new File("test");
FileWriter fw = new FileWriter(file);
fw.append(val)
fw.close();
//Sample BundleFile Writing in Hadoop using Framework

BundleFile file = new BundleFile("test_bundle.seq");
SequenceBundleWriter sbw = new SequenceBundleWriter(file);
sbw.append(himage);
sbw.close();
\end{lstlisting}

@@

//input - HImage is sent as input

CannyEdge canny = new CannyEdge(input);
canny.process();
HImage himage = canny.getProcessedImage();
himage.setImageHeader(input.getImageHeader());

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\textwidth]{files-chart2}
  \caption{Comparing file writers and readers with and without using
    framework}
  \label{fig:files-chart}
\end{figure}
\newpage
\begin{lstlisting}[caption = Comparing FileWriter instance in java and SequenceBundleWriter instance in Hadoop Image Processing framework ]

//Sample File Writing in Java
File file = new File("test");
FileWriter fw = new FileWriter(file);
fw.append(val)
fw.close();

//Sample BundleFile Writing in Hadoop using Framework
BundleFile file = new BundleFile("test_bundle.seq");
SequenceBundleWriter sbw = new SequenceBundleWriter(file);
sbw.append(himage);
sbw.close();
\end{lstlisting}

@@

//input - HImage is sent as input 
CannyEdge canny = new CannyEdge(input);
canny.process();
HImage himage = canny.getProcessedImage();
himage.setImageHeader(input.getImageHeader());
